A unified model for parsing and sentence understanding

### 2016-03-14 writing/hard_stack_paper/paper.tex
Add messy runtime plot

%%% Custom additions %%%
\usepackage{url}
\usepackage[leqno, fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{qtree}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{ifthen}
\usepackage{framed}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

>>>>

%%% Custom additions %%%
\usepackage{url}
\usepackage[leqno, fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{qtree}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{pgfplots}
\usepackage{ifthen}
\usepackage{framed}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[xlabel=Batch size, ylabel=Feedforward time (sec),
			 legend style={anchor=north west}]
  \addplot table [x={Batch size}, y=CPU, col sep=tab] {runtime.csv};
  \addlegendentry{CPU}
  \addplot table [x={Batch size}, y=GPU, col sep=tab] {runtime.csv};
  \addlegendentry{Thin-stack GPU}
\end{axis}
\end{tikzpicture}
\caption{Runtime performance results with the thin-stack GPU algorithm for tree-structured neural networks. \todo{[JG] Add some comments, avg points, add larger batch sizes for thin-stack}}
\end{figure}
